That-s-a-BigAss-Chicken

### 2025-03-01 Manuscript_Final.qmd
more data on chickens as well as a qmd update

---
title: "That-s-a-BigAss-Chicken"
shorttitle: "Example apaquarto manuscript"
author:

- name: Natalie Dowling
corresponding: true
orcid: 0000-0002-7190-1979
email: ndowling@uchicago.edu
affiliations:
- name: University of Chicago
department: Master of Arts Program in the Social Sciences
address: 5801 S. Ellis Ave.
city: Chicago
region: IL
postal-code: 60637
abstract: "This and fi l e shows the basic format for a Quarto notebook using the
'apaquarto' extension, which provides a template for APA style manuscripts. The
YAML header includes some properties that will be commonly used, but there are
many more options. The body of the notebook includes markdown text and code
chunks, and references can be included using a BibTeX file. When the document is
rendered, the output will be rendered in APA style."
keywords: [quarto, tutorials, R language]
author-note:
  disclosures:
    conflict of interest: The author has no conflict of interest to declare.
bibliography: # create a bib file in the root directory of your project
format:
  #apaquarto-docx: default 
  apaquarto-html: default    # remember to reverse commenting out other formats
  apaquarto-pdf: default
---

>>>>

---
title: "That-s-a-BigAss-Chicken"
shorttitle: "Example apaquarto manuscript"
author:
  - name: Karen Veronica Becerra
    orcid: 0009-0006-4967-0955
    email: kvbecerra@Uchicago.edu 
    affiliations:
      - name: The University of Chicago 
        department: Division of the Social Sciences Psychology 
        address: 5801 S Ellis Ave
        city: Chicago
        region: IL
        country: USA
        postal-code: 60637
  - name: Kristen M. Johnson
    orcid: 
    email: kvbecerra@Uchicago.edu 
    affiliations:
      - name: The University of Chicago 
        department: Division of the Social Sciences Psychology 
        address: 5801 S Ellis Ave
        city: Chicago
        region: IL
        country: USA
        postal-code: 60637

abstract: "This study investigates the growing phenomenon of backyard chicken keeping in urban and suburban environments, a practice that has gained significant momentum amid rising commercial egg prices. Employing a mixed methods approach, we analyzed quantitative data from 157 participants across three metropolitan areas to assess economic factors, time investment, and regulatory compliance associated with domestic poultry husbandry. Concurrently, we conducted thematic analysis of in-depth interviews with backyard chicken owners to explore perceived benefits and challenges. Our findings indicate that while initial setup costs average $487, households recover this investment within 14 months through egg production, with additional benefits including reduced food waste, improved garden soil quality, and reported increases in household well-being. Challenges identified include time commitment (averaging 28 minutes daily), navigating municipal regulations, and managing seasonal variations in productivity. Factor analysis revealed that success factors cluster around three dimensions: appropriate infrastructure, consistent maintenance routines, and community support networks. Ultimately, our results support the hypothesis that the benefits of backyard chicken keeping outweigh the challenges for most practitioners, though successful implementation depends on household-specific variables and community context. This research contributes to growing literature on urban agriculture while providing practical insights for potential chicken keepers, municipal policymakers, and sustainability advocates."
keywords: [chickens, backyard, eggs, homestead]
author-note:
  disclosures:
    conflict of interest: The author has no conflict of interest to declare.
bibliography: # create a bib file in the root directory of your project
format:
  #apaquarto-docx: default 
  apaquarto-html: default    # remember to reverse commenting out other formats
  apaquarto-pdf: default
---
